\documentclass[letterpaper,12pt]{examdesign}

\usepackage[version=4]{mhchem}
\usepackage{siunitx}
\usepackage{tabu}
\usepackage{wrapfig}
\usepackage[margin=1in]{geometry}

%\ShortKey
\NoKey
\NumberOfVersions{1}

\class{CHEM312-F18}
\examname{Homework 1}

\ContinuousNumbering
\DefineAnswerWrapper{}{}
\NoRearrange

% Header information
\usepackage{fancyhdr}
\pagestyle{fancy}
\rhead{\examname\ \classdata\Alph{version}}
\lhead{\textbf{Name:\enspace}\rule{0.5\textwidth}{0.4pt}}
\rfoot{\textsf{\thepage}}
\chead{}
\lfoot{\key{\color{red}\ttfamily KEY}}
\cfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\sisetup{retain-explicit-plus} % Always show explicit + in SI units

\begin{document}

\begin{examtop}
	\noindent
	\MakeUppercase{\bfseries \examtype}

	\bigskip

	\noindent
This assignment will be scored out of a total of 10 pts. For full credit, show
all work. Answers only with no work will receive no credit. Ensure final
answers are \textbf{clearly} indicated.
\end{examtop}

\begin{shortanswer}
	
	\begin{question}
		{\footnotesize [2 pts.]} Express the molecular mass ($\pm$
		uncertainty) of \ce{HAuCl4*3H2O}.
	\end{question}

	\begin{question}
		{\footnotesize [4 pts.]} Students measured the concentration of
		\ce{HCl} in a solution by titrating with different indicators to
		find the end point.

		\begin{center}
			\begin{tabu} to \linewidth {l
				S[separate-uncertainty,table-format=1.5(5)] c}
				\tabucline[1pt]{-}
				\bfseries Indicator & {\textbf{[HCl] (M)}} &
				\bfseries \# Measurements \\
				\tabucline[1pt]{-}
				1. Bromothymol blue & 0.11026(621) & 4 \\
				2. Methyl red & 0.10980(41) & 5 \\
				3. Bromocresol green & 0.10986(101) & 8 \\
				\tabucline[1pt]{-}
			\end{tabu}
		\end{center}

		Is the difference between indicators 1 and 2 significant at the
		95\% confidence level? What about indicators 2 and 3?
	\end{question}

	\begin{question}
		{\footnotesize [4 pts.]} An unknown sample of \ce{Cu^{2+}} gave
		an absorbance of 0.306 in an atomic absorption analysis. Then,
		\SI{1.00}{\mL} of solution containing \SI{100.0}{ppm}
		\ce{Cu^{2+}} was mixed with \SI{80.0}{\mL} of unknown and the
		mixture was diluted to \SI{100.0}{\mL} in a volumetric flask.
		The absorbance of the new solution was 0.580. Find the initial
		\ce{[Cu^{2+}]} in the unknown.
	\end{question}
\end{shortanswer}
		
\end{document}
